master thesis

### 2018-03-11 Paper - Latex/Paper - Skizze - v3.tex
Paper - cleanup... add more data.. add effect  section in results...

      This database consists of entries of the form: species A (source) interacts with B (target). \\
      We appointed some interactions, where we know from the biological perspective that the species 
      source or target has to be a parasite or a free-living species. These are the following:
      \begin{itemize}
        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
          hasParasite, hostOf
        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
        \item parasite source: parasiteOf, pathogenOf
        \item parasite target: hasParasite, hasPathogen
      \end{itemize}
      \todo{Interactions nochmal prüfen! Darauf basieren unsere Ergebnisse!} \\
      We build two lists: parasites and free-livings, and add the source or targets of an interaction
        to these. \\
      \todo{klar? Oder Beispiel bringen? (Katze isst Maus $\rightarrow$ Katze ist Freilebend)} \\
      % For every interaction from these lists, we get one or two species for our parasite or 
      %   free-living lists.
      \todo{einige spezies nicht mit einbezogen, da sie keine OTT id haben, hier könnte man noch 
        verbessern (future work)}
      \todo{You can find all interaction types here:
        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .} \\ \\

      With this we got $\sim 51000$ (distinct) freeliving species and $\sim 47000$ (distinct) parasite 
        species (see section countings) \todo{ref einfügen}. But we found also  $\sim 57000$ (not 
        distinct) source species and $\sim 810000$ (not distinct) target species without OTT ids. 
        Since we currently use only OTT ids, we could not use this information. \\
      \todo{mehr dazu in section: unknown nodes...}

@@

        \anmerkung{different parameters for different taxa? (Emanuel)} \\ \\

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Unknown leaf nodes}
    Next to the problem of the multifurcation of the tree is the less of data we have for the species.
      For the ancestral state reconstruction, we need information in the leaf nodes. \\
    The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
      (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7\%$). \\
    With this only $\approx 4.3\%$ information in our leaf nodes are

    \todo{einbauen?:} \\
    unused possible species  57 352 (source), \\
    809 993 (target) \\
    \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
      \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)

@@

      We picked a few phyla to evaluate the results from the biological point of view. \\
      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      As we know \todo{ref einfügen} the Chordata are full of free-living species and there are only a 
        few parasites. The algorithm reflects this. We started with 99.83\% free-living species and 
        predicted 99.94\% species as parasites \todo{(inklusive all known nodes)}. Only 0.06\% were 
        predicted as parasites. These few parasites are mostly breeding parasites (brood parasitism) and 
        some individual errors from the GloBI database. \\
      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95\% as 
        parasites. \\
      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 4.18\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]}

      With the Nematoda it looks very different. In the Nematoda its much worse. Here speaks the 
        literature of \todo{x percent} free-living, but we found only 2.63\% of them. The problem at 
        this point, however, is obvious: The parasites have been much more studied and thus we start 
        with only 0.63\% free-living species. Against such a shifted data situation, the algorithm is 
        powerless. And yet the percentage has increased.

@@

      Lets have a look at the same phyla as in the section before: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Chordata are full of free-living species and so we see only a few origins of parasitism. The root
      and mostly all species are predicted as free-living. \\
      In Apicomplexa and the Platyhelminthes are looking fine too. Our algorithm gives us only one loss 
        of parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over 
        mostly all species predicted as parasites. \\
      Nematoda is again full of problems. The rootnode is predicted as a parasite and so we have more 
        losses of parasitism for the less information of free-living species in this phylum. The rest 
        is parasitic \\

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Cross evaluation - leave 100 out}
      We ran the castor algorithm (\todo{10000}) 70 times with leaving 100 randomized free-living or 
        parasitic species out of the input data to see how stable our result is. \\
      What could happen by removing a parasite or free-living of the list?
      \begin{itemize}
        \item It could be a specie, which don't exist in the tree leaf nodes. -> no effect
        \item It could be a specie, which exists in both lists. -> If it was a parasite, it is now 
          free-living, because we prefer parasites. Otherwise we have no effect again. (1053 are possible)
        \item Normal case: We loose information, because its a specie in our tree and we change it to a 
          leave node with no information.
      \end{itemize}

      \begin{table}
        \begin{center}
          \begin{tabular}{ |cl||r|r|r|r| }
            \hline
            & & min & max & mean & variance ($\sigma^2$) & $\sigma$ \\
            \hline \hline
            \multirow{3}{*}{distance} & all   & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
            & leaf nodes                      & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
            & internal nodes                  & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
            \multicolumn{2}{|c||}{changed tag} & 0 & 0 & 0 & 0 & 0 \\ \hline
            \multirow{3}{*}{lost} & all tags  & 100 & 100 & 100 & 0 & 0 \\
            & FL tags                         & 44 & 66 & 57.25 & 19.50 & 4.42 \\
            & P tags                          & 34 & 56 & 42.75 & 19.50 & 4.42 \\
            \hline
          \end{tabular}
        \end{center}
        \caption{Statistics to Cross validation}
      \end{table}

@@

@@

>>>>

      This database consists of entries of the form: species A (source) interacts with B (target). \\
      We appointed some interactions, where we know from the biological perspective that the species 
      source or target has to be a parasite or a free-living species. These are the following:
      \begin{itemize}
        \item free-living source: preysOn, eats, flowersVisitedBy, hasPathogen, pollinatedBy, 
          hasParasite, hostOf
        \item free-living target: preyedUponBy, parasiteOf, visitsFlowersOf, pathogenOf, hasHost
        \item parasite source: parasiteOf, pathogenOf
        \item parasite target: hasParasite, hasPathogen
      \end{itemize}
      We build two lists: parasites and free-livings, and add the source or targets of an interaction
        to these. \\
      % For every interaction from these lists, we get one or two species for our parasite or 
      %   free-living lists.

      \todo{You can find all interaction types here:
        https://github.com/jhpoelen/eol-globi-data/blob/master/eol-globi-lib/src/main/java/org/eol/globi/domain/InteractType.java .}

@@

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Unknown leaf nodes}
    Next to the problem of the multifurcation of the tree is the less of data we have for the species.
      For the ancestral state reconstruction, we need information in the leaf nodes. \\
    The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
      (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7\%$). \\
    We found also $57,352$ (not distinct) source species and $809,993$ (not distinct) target
      species without OTT ids. Since we currently use only OTT ids, we could not use this information. \\
    \todo{With this only $\approx 4.3\%$ information in our leaf nodes are ...} \\
    We also compared different models in terms of their BICs (Table: \ref{table:BIC unknown information}). 
      The Residuals are not very meaningful here, since all models have different dimensions.

      % Model 1: globi.data ~ kingdom + depth
      % Model 2: globi.data ~ kingdom * depth
      %   Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
      % 1   2297502     544789
      % 2   2297499     544062  3   727.05 < 2.2e-16 ***

      % Model 1: globi.data ~ phylum + depth
      % Model 2: globi.data ~ phylum * depth
      % Resid. Df Resid. Dev Df Deviance  Pr(>Chi)
      % 1   2297453     493017
      % 2   2297406     488366 47   4650.8 < 2.2e-16 ***

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            multifurc $\sim$ taxa & 545799 & 500004 & 485121 & XXXXX\\
            \hline
            multifurc $\sim$ taxa + depth & 544862 & 493808 & XXXXX & XXXXX \\
            \hline
            multifurc $\sim$ taxa * depth & 544179 & 489845 & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BIC of unknown information}
        \label{table:BIC unknown information} 
      \end{table}

@@

      We picked a few phyla to evaluate the results from the biological point of view. \\
      Table \ref{table:phylum leaf nodes states} shows some known phyla: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Since GloBI is not perfect, all examples contain a few bugs.
      As known the Chordata are full of free-living species and there are only a few parasites. Among 
        the birds are some breeding parasites (brood parasitism) like the cuckoo and clepto-parasites as 
        the skuas \cite{Rothschild1957}. The algorithm reflects this. We started with 99.83\% 
        free-living species and predicted 99.94\% species as parasites \todo{(inklusive all known nodes)}. 
        Only 0.06\% were predicted as parasites. \\
      \todo{We found the cuckoo and some skuas...?} \\
      Same observation but with less free-livings is the Apicomplexa Phylum. Here we have only a few 
        free-livings \todo{ref einfügen}. And as we see, we had good start data and predicted 00.95\% as 
        parasites. \\
      For the Platyhelminthes the literature says that there are mostly all Platyhelminthes parasites
        \todo{ref einfügen}. But at the end we predicted 4.18\% as free-living. The class Seriata is the 
        reason for the most of free-livings in this phylum. These are partly free-living flatworms, so 
        the prediction looks right. \\
        \todotext{ Wiki: \\
        *The Seriata are an order of turbellarian flatworms.[1][2] \\
        They are found in both freshwater and marine environments, and also include a number of species 
        found in damp terrestrial conditions. Most are free-living, but the group includes the genus 
        Bdelloura, which lives comensally on the gills of horseshoe crabs. Seriatans are distinguished 
        from other related groups by the presence of a folded pharynx and of a number of diverticula 
        arising from the intestine. The intestine itself may be either simple or branched.[3]}

      With the Nematoda it looks very different. In the Nematoda its much worse. Most Nematoda are 
        free-living, but we found only 2.63\% of them. Blaxter et al. speaks of at least seven 
        independently arosed parasitism \cite{Blaxter1998}. \\
        The problem at this point, however, is obvious: The parasites have been much more studied and 
        thus we start with only 0.63\% free-living species. Against such a shifted data situation, the 
        algorithm is almost powerless. And yet the percentage has increased.

@@

      Lets have a look at the same phyla as in the section before: Chordata, Nematoda, 
        Platyhelminthes and Apicomplexa. \\
      Chordata are full of free-living species and so we see only a few origins of parasitism. The root
      and mostly all species are predicted as free-living. \\
      In Apicomplexa and the Platyhelminthes are looking fine too. Our algorithm gives us only one loss 
        of parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over 
        mostly all species predicted as parasites. \\
      Nematoda is again full of problems. The rootnode is predicted as a parasite and so we have more 
        losses of parasitism for the less information of free-living species in this phylum. The rest 
        is parasitic \\
        As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
          \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
          losses would have to turn around and become Origins. So it could be that we end up in a similar 
          size as Blaxter.

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Cross evaluation - leave 100 out}
      We ran the castor algorithm 100 times with leaving 100 randomized free-living or parasitic species 
        out of the input data to see how stable our result is. Of these 10,000 nodes, 9,238 were unique. 
        Of that, we predicted 9060 ($\approx 98.17\%$) correctly and 169 ($\approx 1.82\%$) wrongly, with 
        duplicate draws always having the same prediction. \\
      What is the best way to model this data? We again tested the influence of the taxa and the depth of 
        leaf nodes and calculated the BICs (Table: \ref{table:BIC cross validation}).

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r|r|r|r| }
            \hline
            Model / Taxa & Kingdom & Phylum & Class & Order \\
            \hline \hline
            correct predicted $\sim$ taxa & 117936 & 112242 & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa + depth & 117776 & XXXXX & XXXXX & XXXXX \\
            \hline
            correct predicted $\sim$ taxa * depth & XXXXX & XXXXX & XXXXX & \cellcolor{green!60}XXXXX \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{BICs of cross validation prediction}
        \label{table:BIC cross validation} 
      \end{table}

      Resiudals:
      \begin{itemize}
        \item correct predicted $\sim$ 1: 120325
        \item correct predicted $\sim$ kingdom: 117877
        \item correct predicted $\sim$ phylum: 111466
      \end{itemize}

      What could happen by removing a parasite or free-living of the list?
      \begin{itemize}
        \item It could be a specie, which don't exist in the tree leaf nodes. -> no effect
        \item It could be a specie, which exists in both lists. -> If it was a parasite, it is now 
          free-living, because we prefer parasites. Otherwise we have no effect again. (1053 are possible)
        \item Normal case: We loose information, because its a specie in our tree and we change it to a 
          leave node with no information.
      \end{itemize}

      Influence on the rest of the data:
      \begin{table}
        \begin{center}
          \begin{tabular}{ |cl||r|r|r|r|r| }
            \hline
            & & min & max & mean & variance ($\sigma^2$) & $\sigma$ \\
            \hline \hline
            \multirow{3}{*}{distance} & all   & 0 & 3587.70 & 224.96 & 313650.61 & 560.05 \\
            & leaf nodes                      & 0 & 3021.12 & 208.69 & 248103.38 & 498.10 \\
            & internal nodes                  & 0 & 566.58 & 16.28 & 4927.95 & 70.20 \\ \hline
            \multicolumn{2}{|c||}{changed tag} & 0 & 0 & 0 & 0 & 0 \\ \hline
            \multirow{3}{*}{lost} & all tags  & 100 & 100 & 100 & 0 & 0 \\
            & FL tags                         & 44 & 66 & 57.25 & 19.50 & 4.42 \\
            & P tags                          & 34 & 56 & 42.75 & 19.50 & 4.42 \\
            \hline
          \end{tabular}
        \end{center}
        \caption{Statistics to Cross validation}
      \end{table}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Effects of Taxa in the different models}

    \anmerkung{different parameters for different taxa? (Emanuel) -> Effects...} \\ \\

    The comparisons of the effects of the taxa can be found in Table \ref{table:Effects unknown data} 
    and showed ...

    \begin{table}[h!]
      \begin{center}
        \begin{longtable}{ |l|l|r|r|r| }
          \hline
          \multicolumn{2}{|c|}{Taxa / Model} & globi $\sim$ taxa & globi $\sim$ taxa + depth & globi $\sim$ taxa * depth\\
          \hline \hline
          Kingdom & no kingdom  & 0.007608091 & 0.009900630 & 0.0004645054 \\
          & Fungi               & 0.011317000 & 0.013723310 & 0.0064413062 \\
          & Chloroplastida      & 0.008634310 & 0.008018847 & 0.0058472786 \\
          & Metazoa             & 0.035634187 & 0.034139782 & 0.0343237575 \\
          \hline
          Phylum & no phylum    & 1.569769e-02 & 3.001749e-02 & 5.757839e-03 \\
          & Rhombozoa           & 1.538462e-02 & 4.128162e-02 & 1.000000e+00 \\
          & Hemichordata        & 1.736770e-07 & 3.791496e-07 & 1.736742e-07 \\
          & Chromerida          & 1.736770e-07 & 4.605436e-07 & 2.220446e-16 \\
          & Amoebozoa           & 5.343198e-03 & 1.312565e-02 & 2.401619e-03 \\
          & Onychophora         & 1.736770e-07 & 3.663718e-07 & 1.736753e-07 \\
          & ... & ... & ... & ... \\
          % & Priapulida          & 4.347826e-02 & 8.773029e-02 \\
          % & Tardigrada          & 1.736770e-07 & 3.393298e-07 \\
          % & Chordata            & 1.140600e-01 & 8.242171e-02 \\
          % & Xanthophyceae       & 1.736770e-07 & 3.483928e-07 \\
          % & Haptophyta          & 3.484321e-03 \\
          % & Microsporidia       & 8.703271e-02 \\
          % & Chytridiomycota     & 3.062361e-02 \\
          % & Nematomorpha        & 1.495017e-02 \\
          % & Loricifera          & 1.736770e-07 \\
          % & Gnathostomulida     & 1.736770e-07 \\
          % & Myzostomida         & 4.464286e-03 \\
          % & Gastrotricha & 1.736770e-07 \\
          % & Ciliophora & 8.372371e-03 \\
          % & Entoprocta & 1.736770e-07 \\
          % & Glomeromycota & 6.609385e-04 \\
          % & Nematoda & 1.098682e-01 \\
          % & Cycliophora & 1.736770e-07 \\
          % & Apicomplexa & 1.374128e-01 \\
          % & Ascomycota & 1.232671e-02 \\
          % & Bryozoa & 4.194290e-03 \\
          % & Nemertea & 9.465855e-03 \\
          % & Echinodermata & 1.971448e-02 \\
          % & Rotifera & 8.638563e-03 \\
          % & Picozoa & 1.736770e-07 \\
          % & Phaeophyceae & 1.219884e-03 \\
          % & Acanthocephala & 3.935018e-01 \\
          % & Bacillariophyta & 4.757374e-05 \\
          % & Colponemidia & 1.736770e-07 \\
          % & Platyhelminthes & 3.127011e-01 \\
          % & Entorrhizomycota & 1.736770e-07 \\
          % & Chaetognatha & 2.941176e-02 \\
          % & Placozoa & 1.736770e-07 \\
          % & Euglenida & 1.729107e-03 \\
          % & Arthropoda & 2.506545e-02 \\
          % & Basidiomycota & 6.149777e-03 \\
          % & Cnidaria & 1.928587e-02 \\
          % & Ctenophora & 4.205607e-02 \\
          % & Kinorhyncha & 1.736770e-07 \\
          % & Porifera & 7.720212e-03 \\
          % & Orthonectida & 1.153846e-01 \\
          % & Mollusca & 9.876095e-03 \\
          % & Brachiopoda & 6.920415e-03 \\
          % & Haplosporida & 8.108108e-02 \\
          % & Rhodophyta & 1.971220e-04 \\
          % & Streptophyta & 8.901842e-03 \\
          % & Foraminifera & 3.395201e-04 \\
          % & Chlorophyta & 3.084992e-04 \\
          \hline \hline
          \multicolumn{2}{|c|}{Taxa / Model} & correct predicted & correct predicted & correct predicted \\
          \multicolumn{2}{|c|}{} & $\sim$ taxa & $\sim$ taxa + depth & $\sim$ taxa * depth\\
          \hline \hline
          Kingdom & no kingdom  & 0.001139888 & ... & ... \\
          & Fungi               & 0.001789739 & ... & ... \\
          & Chloroplastida      & 0.001251109 & ... & ... \\
          & Metazoa             & 0.005414443 & ... & ... \\
          % \hline
          % Phylum & no phylum    & XXXXX & 3.001749e-02 & 5.757839e-03 \\
          % & Rhombozoa           & XXXXX & 4.128162e-02 & 1.000000e+00 \\
          % & Hemichordata        & XXXXX & 3.791496e-07 & 1.736742e-07 \\
          % & Chromerida          & XXXXX & 4.605436e-07 & 2.220446e-16 \\
          % & Amoebozoa           & XXXXX & 1.312565e-02 & 2.401619e-03 \\
          % & Onychophora         & XXXXX & 3.663718e-07 & 1.736753e-07 \\
          % & ... & ... & ... & ... \\
          \hline
        \end{longtable} 
      \end{center}
      \caption{Effects of Taxa in models for unknown data}
      \label{table:Effects unknown data} 
    \end{table}

    globi $\sim$ taxa * depth: NOTE: kingdom is not a high-order term in the model

%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
%                       1.023682e-02                       2.297956e-01
%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
%                       8.586035e-02                       3.000311e-02
%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
%                       3.538708e-07                       3.160858e-07
%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
%                       9.396517e-03                       3.335103e-07
%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
%                       2.114329e-02                       3.281554e-07
%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
%                       1.687966e-03                       1.582959e-01
%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
%                       3.160858e-07                       2.849943e-01
%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
%                       2.217673e-02                       7.020371e-03
%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
%                       1.640797e-02                       3.399753e-02
%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
%                       1.516272e-02                       6.032169e-07
%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
%                       2.014280e-03                       5.672835e-01
%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
%                       1.048765e-04                       5.155971e-07
%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
%                       4.271198e-01                       4.449469e-07
%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
%                       5.936368e-02                       4.965510e-07
%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
%                       4.727403e-03                       1.935197e-02
%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
%                       1.149917e-02                       3.192464e-02
%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
%                       1.077673e-01                       3.540771e-07
%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
%                       1.613863e-02                       2.716252e-01
%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
%                       1.372700e-02                       1.079344e-02
%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
%                       1.925711e-01                       5.358571e-04
%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
%                       6.529378e-03                       7.447417e-04
%       ['ott979501', 'Chlorophyta']
%                       7.296356e-04

% ['ott1085175', 'Priapulida']        ['ott111438', 'Tardigrada']
%                       1.000000e+00                       1.736778e-07
%          ['ott125642', 'Chordata']     ['ott151001', 'Xanthophyceae']
%                       1.138205e-01                       1.736786e-07
%        ['ott151014', 'Haptophyta']      ['ott16113', 'Microsporidia']
%                       1.000000e+00                       9.998257e-01
%   ['ott177160', 'Chytridiomycota']      ['ott189836', 'Nematomorpha']
%                       1.000000e+00                       2.220446e-16
%        ['ott199402', 'Loricifera']   ['ott242963', 'Gnathostomulida']
%                       2.220446e-16                       2.220446e-16
%       ['ott260040', 'Myzostomida']       ['ott29723', 'Gastrotricha']
%                       4.381889e-06                       1.736782e-07
%        ['ott302424', 'Ciliophora']        ['ott362916', 'Entoprocta']
%                       5.518629e-05                       1.736802e-07
%     ['ott385878', 'Glomeromycota']          ['ott395057', 'Nematoda']
%                       9.966669e-01                       4.725574e-01
%        ['ott41147', 'Cycliophora']       ['ott422673', 'Apicomplexa']
%                       2.220446e-16                       8.049756e-01
%        ['ott439373', 'Ascomycota']           ['ott442934', 'Bryozoa']
%                       1.541511e-02                       1.230174e-03
%          ['ott445195', 'Nemertea']     ['ott451020', 'Echinodermata']
%                       1.777755e-01                       2.505179e-03
%          ['ott471706', 'Rotifera']          ['ott4738955', 'Picozoa']
%                       3.125183e-01                       1.736782e-07
%       ['ott48614', 'Phaeophyceae']     ['ott49622', 'Acanthocephala']
%                       9.252076e-04                       3.992551e-04
%  ['ott5342311', 'Bacillariophyta']     ['ott5355158', 'Colponemidia']
%                       1.114784e-10                       2.220446e-16
%   ['ott555379', 'Platyhelminthes'] ['ott5653719', 'Entorrhizomycota']
%                       2.478056e-02                       1.736781e-07
%      ['ott570366', 'Chaetognatha']          ['ott570376', 'Placozoa']
%                       1.000000e+00                       4.021433e-08
%        ['ott6137051', 'Euglenida']        ['ott632179', 'Arthropoda']
%                       9.257999e-01                       1.658528e-02
%     ['ott634628', 'Basidiomycota']          ['ott641033', 'Cnidaria']
%                       1.473459e-03                       1.218008e-02
%        ['ott641212', 'Ctenophora']       ['ott677389', 'Kinorhyncha']
%                       2.878555e-03                       1.736844e-07
%           ['ott67819', 'Porifera']      ['ott691845', 'Orthonectida']
%                       1.329787e-02                       2.931611e-02
%          ['ott802117', 'Mollusca']       ['ott826261', 'Brachiopoda']
%                       5.167513e-03                       9.974617e-01
%      ['ott858063', 'Haplosporida']        ['ott878953', 'Rhodophyta']
%                       9.999999e-01                       9.658119e-11
%      ['ott916750', 'Streptophyta']      ['ott936399', 'Foraminifera']
%                       6.037565e-03                       6.367782e-03
%       ['ott979501', 'Chlorophyta']
%                       2.027010e-05

@@

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
\chapter{Komplett aussortierte Tabellen etc}
